Add Plant Functional Type (PFT) labels

### 2021-04-22 R/add_plant_functional_type.Rmd
working on taxon laebls

  else if(genusSpecies == "Juglans nigra"){
    taxon_pft_lookup$pft_MRA[i] = "deciduous_forest"
    taxon_pft_lookup$pft_MODIS[i] = ""
    taxon_pft_lookup$phenology[i] = ""
    taxon_pft_lookup$leafType[i] = ""
    taxon_pft_lookup$growthForm[i] = ""
    taxon_pft_lookup$commonName[i] = "black walnut"}

  else if(genusSpecies == "Juniperus osteosperma"){
    taxon_pft_lookup$pft_MRA[i] = "coniferous_forest"
    taxon_pft_lookup$pft_MODIS[i] = ""
    taxon_pft_lookup$phenology[i] = ""
    taxon_pft_lookup$leafType[i] = ""
    taxon_pft_lookup$growthForm[i] = ""
    taxon_pft_lookup$commonName[i] = "Utah juniper"}

  else if(genusSpecies == "Juniperus virginiana"){
    taxon_pft_lookup$pft_MRA[i] = "coniferous_forest"
    taxon_pft_lookup$pft_MODIS[i] = ""
    taxon_pft_lookup$phenology[i] = ""
    taxon_pft_lookup$leafType[i] = ""
    taxon_pft_lookup$growthForm[i] = ""
    taxon_pft_lookup$commonName[i] = "red cedar"}

  else if(genusSpecies == "Larix sp."){
    taxon_pft_lookup$pft_MRA[i] = "coniferous_forest"
    taxon_pft_lookup$pft_MODIS[i] = ""
    taxon_pft_lookup$phenology[i] = ""
    taxon_pft_lookup$leafType[i] = ""
    taxon_pft_lookup$growthForm[i] = ""
    taxon_pft_lookup$commonName[i] = "larch"}

>>>>

  else if(genusSpecies == "Juglans nigra"){
    taxon_pft_lookup$pft_MRA[i] = "deciduous_forest"
    taxon_pft_lookup$pft_MODIS[i] = "deciduous-broadleaf_forest"
    taxon_pft_lookup$phenology[i] = "deciduous"
    taxon_pft_lookup$leafType[i] = "broadleaf"
    taxon_pft_lookup$growthForm[i] = "tree"
    taxon_pft_lookup$commonName[i] = "black walnut"}

  else if(genusSpecies == "Juniperus osteosperma"){
    taxon_pft_lookup$pft_MRA[i] = "coniferous_forest"
    taxon_pft_lookup$pft_MODIS[i] = "evergreen_needleleaf_forest"
    taxon_pft_lookup$phenology[i] = "evergreen"
    taxon_pft_lookup$leafType[i] = "needleleaf" # scale-like needle leaves
    taxon_pft_lookup$growthForm[i] = "tree"
    taxon_pft_lookup$commonName[i] = "Utah juniper"}

  else if(genusSpecies == "Juniperus virginiana"){
    taxon_pft_lookup$pft_MRA[i] = "coniferous_forest"
    taxon_pft_lookup$pft_MODIS[i] = "evergreen_needleleaf_forest"
    taxon_pft_lookup$phenology[i] = "evergreen"
    taxon_pft_lookup$leafType[i] = "needleleaf" # scale-like needle leaves
    taxon_pft_lookup$growthForm[i] = "tree"
    taxon_pft_lookup$commonName[i] = "red cedar"}

  else if(genusSpecies == "Larix sp."){
    taxon_pft_lookup$pft_MRA[i] = "coniferous_forest"
    taxon_pft_lookup$pft_MODIS[i] = "deciduous-needleleaf_forest"
    taxon_pft_lookup$phenology[i] = "deciduous" # larch is an unusual genus with deciduous conifers
    taxon_pft_lookup$leafType[i] = "needleleaf"
    taxon_pft_lookup$growthForm[i] = "tree"
    taxon_pft_lookup$commonName[i] = "larch"}
